Displacement of fishing effort by Large Scale Marine Protected Areas

### 2018-09-29 docs/Manuscript.tex
Added changes after proof reading, waiting for spatial analysis to be done before sending it out to John

@@

This section is divided into two main parts. First, we provide a general
description of AIS data and the process of identification of
vessel-level events done by Global Fishing Watch\footnote{Global Fishing
  Watch: \url{globalfishingwatch.org}}. Alongside, we describe the
subset of data that we use for these analyses. When relevant, we also
point out possible shortcommings in the data, or factors that must be
considered in the later analyses. Then we move on to explain our
identification strategy, and the main analyses that we undertake.

@@

\subsubsection{AIS data}\label{ais-data}

Automatic Identification Systems are on-board devices intended to
provide at-sea saftey and prevent ship collisions by broadcasting vessel
locations to surrounding vessels. These broadcasted positions can be
recorded by satellites and land-based antenas. GFW uses a neural network
to infer vessel characteristics and whether each broadcasted position
represents a fishing event, thus allowing us to estimate near real-time
fishing events globally since 2012 \citep{kroodsma_2018}. The recent
addition of satellites that can receive AIS signals causes an apparent
increase in the number of broadcasted AIS messages (\emph{i.e.} points)
and therefore fishing hours. The variability in AIS data and ocean
conditions require that temporal trends be taken into account. We do
that by incorporating a series of controls, which are defined in the
following section.

\subsubsection{PIPA data}\label{pipa-data}

Our data contain over 45 million individual AIS messages for 371 purse
seiners and longliners. A total of 233 vessels have fished within PIPA
waters; 217 did so at least once before 2015. However, not all vessels
continued to fish elsewhere after PIPA implementation: 34 vessels have
no recorded AIS messages after 2015\footnote{The 0 missing vessels might
  have exited the fishery, been decomissioned or sold (therefore
  changing their AIS and mmsi), or turned off their AIS transmiters. In
  either case, we are not able to observe these.}, leaving us with 183
vessels that fished inside PIPA before its implementation, and continued
to fish elsewhere afterward. Vessels that fished within PIPA before
implementation might stop fishing afterwards, therefore not being
observable in the post-treatment period. New vessels might have also
entered the fishery after PIPA closure, and were likely not exposed to
the policy intervention in the pre-treatment period. Therefore, we
define our treatment and control groups as follows.

The treatment group contains all vessels (n = 183) that fished within
PIPA at least once before the closure, and that continued to fish
elsewhere afterwards. Vessels in the control group meet al three of the
following conditions: i) Vessels never fished within PIPA waters, ii)
vessels belong to other PNA countries, and iii) vessels have fished in
surrounding areas (\emph{i.e.} PNA-countries' EEZ) before and after PIPA
closure. For each vessel meeting these characteristics, we calculate
their total monthly fishing hours. Figure \ref{fig:baci_strict} provides
a visual representation of the vessel-level streams of fishing events
that make up each group through time. Tables \ref{tab:baci_n_s} and
\ref{tab:baci_h} show the number of vessels following a BACI design, and
fishing hours, respectively. Tables show data grouped by gear
(longlines, purse seines), group (treated, control), and period (before,
after). The relative change in fishing hours (After / Before) is also
shown.

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{\label{fig:unnamed-chunk-4}\label{fig:baci_strict}Stream of fishing
events by vessels through time. Each line represents a vessel, with dots
indicating months with fishing activity and colors indicating the pre
and post periods. Pannels separating between gear and treated or control
groups.}
\end{figure}

@@

\caption{\label{tab:unnamed-chunk-5}\label{tab:baci_n_s}Number of fishing vessels (identified by mmsi) by gear and treatment group.}
\centering
\begin{tabular}[t]{llr}
\toprule
Gear & Treatment & n\\
\midrule
drifting\_longlines & FALSE & 85\\
drifting\_longlines & TRUE & 115\\
purse\_seines & FALSE & 36\\
purse\_seines & TRUE & 68\\
\bottomrule
\end{tabular}
\end{table}

\caption{\label{tab:unnamed-chunk-6}\label{tab:baci_h}Mean fishing hours and relative change by gear and treatment group.}
\centering
\begin{tabular}[t]{llrrr}
\toprule
Gear & Treatment & Before & After & Change (A / B)\\
\midrule
drifting\_longlines & FALSE & 474.47780 & 462.5491 & 0.9748593\\
drifting\_longlines & TRUE & 544.61935 & 522.8392 & 0.9600085\\
purse\_seines & FALSE & 59.49026 & 154.5776 & 2.5983673\\
purse\_seines & TRUE & 52.91534 & 131.5452 & 2.4859561\\
\bottomrule
\end{tabular}
\end{table}

@@

Where \(y_{i,t}\) is the variable of interest for vessel \(i\) in time
period \(t\). A dummy variable \(Post_i\) takes the value of 0 for all
dates prior to PIPA implementation and a value of 1 por all dates
including and following PIPA implementation. \(Treat_i\) is a dummy
variable indicating whether a vessel belongs to the control
(\(Treat_i = 0\)) or treatment (\(Treat_i = 1\)) group. \(\alpha\) is
the standard intercept, \(\beta_1\) captures the \emph{ex post} change,
\(\beta_2\) captures the difference between treated and control groups,
and \(\beta_3\) is our parameter of interest: de DiD estimate capturing
the treatment effect. Finally, \(\mu_1\) and \(\mu_2\) are coefficients
for a second order polynomial for years (\(Y_t\))\footnote{An earlier
  specification included years as a dummy variable. Such results are
  included in the appendx.}, while \(\phi_t\) and \(\gamma_i\) represent
month-, and flag-level dummies that account for seasonality or
country-level management interventions.

Our second part of the analyses focuses on the redistribution of fishing
effort. In other words, identifying where do vessels that used to fish
inside PIPA go after its establishment. We calculate the monthly
relative distribution of fishing hours by all treated vessels across all
fished EEZs and the high seas. These trends are shown in Figures
\ref{fig:redist_trend_ps} and \ref{fig:redist_trend_ll}, and the
relative change is presented in Table \ref{tab:ba_disp}. EEZs that had
sproadic fishing events were pooled into a group of ``others'', leaving
us with a total of n = 12 and n = 10 spatially defined regions
(\emph{i.e.} EEZs, High Seas, ``other EEZs'') for purse seiners and
longliners, respectively.

To evaluate this change in effort allocation, we regress our variable of
interest, fishing hours, on the interaction between a dummy variable
indicating the policy intervention and a dummy variable for countries,
to obtain the by-country change in proportional allocation of fishing
effort:

\[
y_{i,t} = \alpha + \beta_1Post_t + \beta_2Country_i + \beta3Post_t \times Country_i + \epsilon_{i,t}
\]

Our variable of interest, \(y_{i,t}\) represents the proportion of
fishing hours that country \(i\) receives at time \(t\). \(Post\) also
represents a policy dummy that takes the value of 0 for all dates before
implementation of PIPA, and 1 otherwise. \(Country\) is a dummy variable
for countries, interpreted as individual EEZs, the high seas, and a
group of ``other EEZs''. Our parameter of interest is \(\beta_3\), which
captures the country-level change in proportional fishing effort.

All regression coefficients were estimatedd via ordinary least squares,
and heteroskedastic-robust standard errors were calculated. All analyses
were performed in R version 3.5.1) \citep{rcore_2018}. Raw data and code
used in this work are available on
\href{https://github.com/jcvdav/MPA_displacement}{github}.

@@

\caption{\label{tab:unnamed-chunk-9}\label{tab:ba_disp}}
\centering
\begin{tabular}[t]{lrr}
\toprule
country & Longliners & Purse seiners\\
\midrule
PIPA & -11.48 & -8.54\\
KIR & 1.28 & 2.76\\
HS & 0.00 & 0.00\\
COK & 0.00 & 0.34\\
FSM & 0.00 & 0.55\\
\addlinespace
MHL & NA & -0.55\\
NRU & 0.00 & 0.16\\
PNG & 0.00 & -10.02\\
SLB & -8.48 & 2.13\\
TKL & NA & 0.19\\
\addlinespace
TUV & 7.23 & 1.47\\
others & 22.55 & 11.51\\
\bottomrule
\end{tabular}
\end{table}

@@

Our data suggest that purseiners and longliners have different responses
to the implementation of a Large-Scale Marine Protected Area. Fig.
\ref{fig:all_vessels} shows that mean fishing hours for purse seiners
have an abrupt increase, just before January 1st, 2015. This trend is
observed for both treated and control groups. Longliners, however, show
a more stable trend. The number of mmsi codes increases through time.
This can largely be explained by the addition of more satellites, which
increase detectability of vessels. As expected, total fishing hours
follow a similar trend to that of mmsi numbers.

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}
\caption{\label{fig:unnamed-chunk-10}\label{fig:all_vessels}Fishing hours
and number of vessels by month for all vessels. Vertical dashed line
indicates PIPA closure.}
\end{figure}

Our DiD anaylsis shows that treated purse seiners reduce their fishing
effort after PIPA implementation in the order of 16 hours per month.
This result is robust and significant (\emph{p \textless{} 0.05}) for
all model specifications, with the effect varying between
\(\beta_3 = -16.457\) and \(\beta_3 = -18.709\). Model specifications
that include the year polynomial show lower values for the \(\beta_1\)
coefficient associated to the \(Post_t\) policy dummy, and show positive
and negative values for \(\mu_1\) and \(\mu_2\), the linear and
cuadratic terms, respectively. These effectively represent the patterns
observed in Figure \{fig:all\_vessels\}.

@@

The change in the relative allocation fishing effort by purse seiners
increases in eight of the 12 regions after PIPA implementation
\ref{tab:disp_mod}. The largest increase is observed for the I-Kiribati
EEZ, with an average increase of 0.11 (\emph{p \textless{} 0.001}). In
other words, the redistribution of treated vessels caused a 10\%
increase in the \emph{relative} allocation of fishing effort within
I-Kiribati waters. The only decrease is observed for Papua New Guinea,
but the coefficient is not significant. Figure \ref{fig:map_change_ps}
provides a spatial representation of these changes. It is evident that
the increase in relative fishing effort is greater for for regions
closer to PIPA.

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-15-1.pdf}
\caption{\label{fig:unnamed-chunk-15}\label{fig:redist_trend_ps}}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-18-1.pdf}
\caption{\label{fig:unnamed-chunk-18}\label{fig:map_change_ps}}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-19-1.pdf}
\caption{\label{fig:unnamed-chunk-19}\label{fig:map_change_ps}}
\end{figure}

\begin{table}[!htbp] \centering 
  \caption{\label{tab:disp_mod}Change in the relative allocation of fishing hours by purse seiners for each region. Asterisks indicate significance levels. Numbers in parenthesis represent heteroskedastic-robust standard errors.} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & h\_prop \\ 
\hline \\[-1.8ex] 
 post & $-$0.085$^{***}$ (0.018) \\ 
  countryKIR & 0.251$^{***}$ (0.036) \\ 
  countryHS & $-$0.089$^{***}$ (0.018) \\ 
  countryCOK & $-$0.085$^{***}$ (0.018) \\ 
  countryFSM & $-$0.034 (0.021) \\ 
  countryMHL & $-$0.063$^{***}$ (0.019) \\ 
  countryNRU & $-$0.039$^{**}$ (0.020) \\ 
  countryPNG & 0.098$^{***}$ (0.034) \\ 
  countrySLB & $-$0.023 (0.026) \\ 
  countryTKL & $-$0.072$^{***}$ (0.018) \\ 
  countryTUV & $-$0.024 (0.021) \\ 
  countryothers & 0.016 (0.021) \\ 
  post:countryKIR & 0.113$^{**}$ (0.045) \\ 
  post:countryHS & 0.085$^{***}$ (0.018) \\ 
  post:countryCOK & 0.089$^{***}$ (0.018) \\ 
  post:countryFSM & 0.091$^{***}$ (0.025) \\ 
  post:countryMHL & 0.080$^{***}$ (0.021) \\ 
  post:countryNRU & 0.087$^{***}$ (0.021) \\ 
  post:countryPNG & $-$0.015 (0.037) \\ 
  post:countrySLB & 0.107$^{***}$ (0.031) \\ 
  post:countryTKL & 0.087$^{***}$ (0.019) \\ 
  post:countryTUV & 0.100$^{***}$ (0.025) \\ 
  post:countryothers & 0.201$^{***}$ (0.028) \\ 
  Constant & 0.089$^{***}$ (0.018) \\ 
 \hline \\[-1.8ex] 
Month FE & No \\ 
Observations & 864 \\ 
R$^{2}$ & 0.557 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

@@

Our findings provide interesting insights into the effect that LSMPAs
can have on vessel behavior and the redistribution of fishing effort.
These collection of results shows that the implementation of PIPA caused
treated vessels to redeuce their fishing hours, and that this effect is
greater for purse seiners. Even though treated vessels fish less, their
relative allocation of fishing hours increased for all other fishing
grouds. This fidnings does not imply that there is more fishing effort,
but rather that each region receives a greater portion of the post-PIPA
fishing effort (which is lower than pre-PIPA). In this section we
discuss the implications of vessel-level reductions in fishing effort
and the increase in relative allocation of the remaining effort through
space. We also provide plausible explanations as to why purse seiners
seem to be more reactive to the spatial closure.

Previous studies on insular environments suggest that vessels move to
distant places, which might be translated as increased costs
\citep{stevenson_2013}. Nevertheless, this study does not use
counterfactuals that could help account for system- or fleet-level
changes that occur through time. Others have used similar
satellite-tracking systems to show that fishing effort accumulates near
the edges ospatial closures, yielding greater catches
\citep{murawski_2005}. Yet, these vessel tracks do not cover the
pre-reserve period, making it difficult identify the contribution of
spatial closures to the observed spatial distribution of fishing
vessels. Recent work by \citet{elahi_2018} identified that total fishing
effort in a focal region where a short-term MPA was implemented showed
little change, likely indicating that fishers redistributed fishing
effort to compensate for the reduction in available space. Our data is
assambled in a similar way, with fishing positions before and after the
implementation of PIPA and vessels grouped into treated and control
groups. Our BACI design, along with our difference-in-differences
analysis allows us to make causal inferences about the effect that large
scale marine protected areas have on fishing effort.

The different responses observed between purse seiners and longliners
might have two possible explanations. It is likely that PIPA did not
contain habitat that longliners would consider optimal. Therefore, the
sporadic fishing events that occurred there are of little importance to
the fleet, and it is unlikely that the implementation of PIPA has an
effect on them. Alternatively, the differences may be due to the nature
of each fishing gear. Purse seiners are often constrained by seafloor
and termocline depth, and often operate in more restricted areas
\citep{kroodsma_2018}. Tuna purse seiners are known to have greater
proportion of null sets (\emph{i.e.} where the purse seine is
effectively casted arround tuna, but no catch is obtained) during El
Niño years, where the termocline deepens in the Eastern Pacific
\citep{dreyfusleon_2015}. On the other hand, longliners may be more
flexible as to where they can deploy their longlines.
\citet{ortuocrespo_2018} evaluated the ecological niche of the pelagic
longline fleet, and suggest that the fleet may be underutilizing the
ocean, meaning that they can easily redistribute elsewhere.

\section{References}\label{references}

\hypertarget{refs}{}

>>>>

Mpas are being implemented like crazy

Debate on LSMPA the devil you know

Where do vessels go is the key part of it

@@

This section is divided into two main parts. First, we provide a general
description of AIS data and the process of identification of
vessel-level fishing events done by Global Fishing Watch\footnote{Global
  Fishing Watch: \url{globalfishingwatch.org}}. Alongside, we describe
the subset of data that we use for these analyses. When relevant, we
also point out possible shortcommings in the data, or factors that must
be considered in the later analyses. We then move on to explain our
empirical strategy for the identification of the behaviorial changes and
redistribution of fishing effort.

@@

Automatic Identification Systems are on-board devices intended to
provide at-sea saftey and prevent ship collisions by broadcasting vessel
position, course, and activities to surrounding vessels. These
broadcasted messages can be received by satellites and land-based
antenas. GFW uses a neural network to infer vessel characteristics and
whether each broadcasted position represents a fishing event, thus
allowing us to estimate near real-time fishing events globally since
2012 \citep{kroodsma_2018}. Our data contain information for 2012 -
2017. The recent addition of satellites that can receive AIS signals
causes an apparent increase in the number of broadcasted AIS messages
(\emph{i.e.} points), and therefore number of vessels and fishing hours.
The variability in AIS data and ocean conditions require that temporal
trends be taken into account. We do that by obtaining a subset of data
that meet a BACI design, which gives us the full tracks for vessels
affected and unaffected by the implementation of PIPA.

Our data contain over 45 million individual AIS messages (\emph{i.e.}
positions) for 371 purse seiners and longliners. A total of 233 vessels
have fished within PIPA waters; 217 did so at least once before 2015.
However, not all vessels continued to fish elsewhere after PIPA
implementation: 34 vessels have no recorded AIS messages after
2015\footnote{The 34 missing vessels might have exited the fishery, been
  decomissioned or sold (therefore changing their AIS and mmsi), or
  turned off their AIS transmiters. In either case, we are not able to
  observe these.}, leaving us with 183 vessels that fished inside PIPA
before its implementation, and continued to fish elsewhere afterward.
New vessels might have also entered the fishery after PIPA closure, and
were likely not exposed to the policy intervention in the pre-treatment
period. To account for this, we identify a subset of vessels which we
track since before the implementation of PIPA, and categorize them as
treated or control vessels. Our treatment and control groups are defined
as follows.

The treatment group contains all vessels (n = 183) that fished within
PIPA at least once before the closure, and that continued to fish
elsewhere afterwards. Vessels in the control group meet all three of the
following conditions: i) vessels never fished within PIPA waters, ii)
vessels belong to other PNA countries, and iii) vessels have fished in
surrounding areas (\emph{i.e.} PNA-countries' EEZ) before and after PIPA
closure. For each vessel meeting these characteristics, we calculate
their total monthly fishing hours. Figure \ref{fig:baci_strict} provides
a visual representation of the vessel-level fishing events that make up
each group through time. Table \ref{tab:baci_n_s} shows the number of
vessels following a BACI design, as well as the fishing hours, before
and after PIPA.

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{\label{fig:unnamed-chunk-4}\label{fig:baci_strict}Stream of fishing
events by vessels through time. Each line represents a vessel, with dots
indicating months with fishing activity and colors indicating the pre
and post periods.}
\end{figure}

@@

\caption{\label{tab:unnamed-chunk-5}\label{tab:baci_n_s}Number of fishing vessels and fishing hours by gear and treatment group before and after PIPA.}
\centering
\begin{tabular}[t]{llrrrr}
\toprule
Gear & Treatment & n & Before & After & Change (A / B)\\
\midrule
drifting\_longlines & FALSE & 85 & 474.47780 & 462.5491 & 0.9748593\\
drifting\_longlines & TRUE & 115 & 544.61935 & 522.8392 & 0.9600085\\
purse\_seines & FALSE & 36 & 59.49026 & 154.5776 & 2.5983673\\
purse\_seines & TRUE & 68 & 52.91534 & 131.5452 & 2.4859561\\
\bottomrule
\end{tabular}
\end{table}

@@

Where \(y_{i,t}\) is the variable of interest for vessel \(i\) in time
period \(t\). A dummy variable \(Post_t\) takes the value of 0 for all
dates prior to PIPA implementation and a value of 1 por all dates
including and following PIPA implementation. \(Treat_i\) is a dummy
variable indicating whether a vessel belongs to the control
(\(Treat_i = 0\)) or treatment (\(Treat_i = 1\)) group. \(\alpha\) is
the standard intercept, \(\beta_1\) captures the temporal trend change,
\(\beta_2\) captures the difference between treated and control groups,
and \(\beta_3\) is our parameter of interest: de DiD estimate capturing
the treatment effect. Finally, \(\mu_1\) and \(\mu_2\) are coefficients
for a second order polynomial for years (\(Y_t\)), while \(\phi_t\) and
\(\gamma_i\) represent month-, and flag-level dummies that account for
seasonality or country-level management interventions\footnote{An
  earlier specification included years as a dummy variable. Such results
  are included in the appendx, but are similar to the ones found under
  current specification.}.

Our second part of the analyses focuses on the redistribution of fishing
effort. In other words, identifying where do vessels that used to fish
inside PIPA go after its establishment. We calculate the monthly
relative distribution of fishing hours by all treated vessels across all
fished EEZs and the high seas. These trends are shown in Figure
\ref{fig:redist_trend_ps}, and the relative temporal change is presented
in Table \ref{tab:ba_disp}. EEZs that had sporadic fishing events were
pooled into a group of ``others'', leaving us with a total of n = 12 and
n = 10\footnote{This number is likely to change upon finalizing the
  spatial analysis of longliners, which is currently running.} spatially
defined regions (\emph{i.e.} EEZs, High Seas, ``other EEZs'', and PIPA)
for purse seiners and longliners, respectively.

To evaluate this change in effort allocation, we regress our variable of
interest (\emph{i.e.}fishing hours) on the interaction between a dummy
variable indicating the policy intervention and a dummy variable for
countries. This gives us the by-country change in proportional
allocation of fishing effort:

\[
y_{i,t} = \alpha + \beta_1Post_t + \beta_{2,i}Country_i + \beta_{3,i}Post_t \times Country_i + \epsilon_{i,t}
\]

Our variable of interest, \(y_{i,t}\) represents the proportion of
fishing hours that country \(i\) receives at time \(t\). \(Post\) also
represents a policy dummy that takes the value of 0 for all dates before
implementation of PIPA, and 1 otherwise. \(Country\) is a dummy variable
for countries, interpreted as individual EEZs, the high seas, and a
group of ``other EEZs''. Our parameter of interest is \(\beta_{3,i}\),
which captures the country-level change in proportional fishing effort.

All regression coefficients were estimatedd via ordinary least squares,
and heteroskedastic-robust standard errors were calculated. All analyses
were performed in R version 3.5.1 \citep{rcore_2018}. Raw data and code
used in this work are available on
\href{https://github.com/jcvdav/MPA_displacement}{github}.

@@

\caption{\label{tab:unnamed-chunk-8}\label{tab:ba_disp}Changes in the relative allocation of fishing effort by region (EEZ, PIPA, high seas) and gear.}
\centering
\begin{tabular}[t]{lrr}
\toprule
country & Longliners & Purse seiners\\
\midrule
PIPA & -11.48 & -8.54\\
KIR & 1.28 & 2.76\\
HS & 0.00 & 0.00\\
COK & 0.00 & 0.34\\
FSM & 0.00 & 0.55\\
\addlinespace
MHL & NA & -0.55\\
NRU & 0.00 & 0.16\\
PNG & 0.00 & -10.02\\
SLB & -8.48 & 2.13\\
TKL & NA & 0.19\\
\addlinespace
TUV & 7.23 & 1.47\\
others & 22.55 & 11.51\\
\bottomrule
\end{tabular}
\end{table}

@@

Our data suggest that purseiners and longliners have different responses
to the implementation of a Large-Scale Marine Protected Areas. Fig.
\ref{fig:all_vessels} shows that mean fishing hours for purse seiners
have an abrupt increase, just before January 1st, 2015. This trend is
observed for both treated and control groups. The pattern closely
corresponds with the increase in total hours, but the total number of
vessels doesn't entirely follow this pattern. The increase in fishing
hours might be caused by the increased number of satellites\footnote{Need
  to check this. Not sure any satellites were incorporated during 2014.
  It is also possible that PNA countries started enforcing the
  requirement of having an AIS unit. On either case, both treatment and
  control groups seem to be affected equally.}. Longliners, however,
show no apparent trend with a clear seasonality
\citep{ortuocrespo_2018}. The number of mmsi codes also increases
slightly through time, but becomes stable after 2015. For both gears and
across all measures, the treatment and control vessels follow similar
patterns, confirming our claim that the control group provides a
plausible counterfactual.

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-9-1.pdf}
\caption{\label{fig:unnamed-chunk-9}\label{fig:all_vessels}Fishing hours and
number of vessels by month for all vessels. Vertical dashed line
indicates PIPA closure.}
\end{figure}

Our DiD anaylsis shows that treated purse seiners reduce their fishing
effort after PIPA implementation in the order of 16 hours per month.
This result is robust and significant (\emph{p \textless{} 0.05}) for
all model specifications, with the effect varying between
\(\beta_3 = -16.457\) and \(\beta_3 = -18.709\). Model specifications
that include the year polynomial show lower values for the \(\beta_1\)
coefficient associated to the \(Post_t\) policy dummy, and show positive
and negative values for \(\mu_1\) and \(\mu_2\), the linear and
cuadratic terms for \(Y_t\), respectively. These effectively represent
the patterns observed in Figure \ref{fig:all_vessels}.

@@

The change in the relative allocation of fishing effort by purse seiners
increases in eight of the 12 regions after PIPA implementation (Table
\ref{tab:disp_mod}). The largest increase is observed for the I-Kiribati
EEZ, with an average increase of 0.11 (\emph{p \textless{} 0.001}). In
other words, the redistribution of treated vessels caused a 10\%
increase in the \emph{relative} allocation of fishing effort within
I-Kiribati waters. The only decrease is observed for Papua New Guinea,
but the coefficient is not significant. Figure \ref{fig:map_change_ps}
provides a spatial representation of these changes. It is evident that
the increase in relative fishing effort is greater for for regions
closer to PIPA.

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-14-1.pdf}
\caption{\label{fig:unnamed-chunk-14}\label{fig:redist_trend_ps}Monthly
relative allocation of fishing effort by PIPA-fishing vessels before and
after PIPA for 9 EEZs, PIPA, the high seas and `other EEZs'.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-17-1.pdf}
\caption{\label{fig:unnamed-chunk-17}\label{fig:map_change_ps}Spatial
representation of the mean change in the monthly allocation of fishing
effort for purse seiners.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-18-1.pdf}
\caption{\label{fig:unnamed-chunk-18}\label{fig:map_change_ps}Spatial
representation of the mean change in the monthly allocation of fishing
effort for longliners. \textbf{This are preliminar results, contingent
on the spatial analysis currently being run}}
\end{figure}

\begin{table}[!htbp] \centering 
  \caption{\label{tab:disp_mod}Change in the relative allocation of fishing hours by purse seiners for each region. Asterisks indicate significance levels. Numbers in parenthesis represent heteroskedastic-robust standard errors.} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & h\_prop \\ 
\hline \\[-1.8ex] 
 post & $-$0.085$^{***}$ (0.018) \\ 
  countryKIR & 0.251$^{***}$ (0.036) \\ 
  countryHS & $-$0.089$^{***}$ (0.018) \\ 
  countryCOK & $-$0.085$^{***}$ (0.018) \\ 
  countryFSM & $-$0.034 (0.021) \\ 
  countryMHL & $-$0.063$^{***}$ (0.019) \\ 
  countryNRU & $-$0.039$^{**}$ (0.020) \\ 
  countryPNG & 0.098$^{***}$ (0.034) \\ 
  countrySLB & $-$0.023 (0.026) \\ 
  countryTKL & $-$0.072$^{***}$ (0.018) \\ 
  countryTUV & $-$0.024 (0.021) \\ 
  countryothers & 0.016 (0.021) \\ 
  post:countryKIR & 0.113$^{**}$ (0.045) \\ 
  post:countryHS & 0.085$^{***}$ (0.018) \\ 
  post:countryCOK & 0.089$^{***}$ (0.018) \\ 
  post:countryFSM & 0.091$^{***}$ (0.025) \\ 
  post:countryMHL & 0.080$^{***}$ (0.021) \\ 
  post:countryNRU & 0.087$^{***}$ (0.021) \\ 
  post:countryPNG & $-$0.015 (0.037) \\ 
  post:countrySLB & 0.107$^{***}$ (0.031) \\ 
  post:countryTKL & 0.087$^{***}$ (0.019) \\ 
  post:countryTUV & 0.100$^{***}$ (0.025) \\ 
  post:countryothers & 0.201$^{***}$ (0.028) \\ 
  Constant & 0.089$^{***}$ (0.018) \\ 
 \hline \\[-1.8ex] 
Observations & 864 \\ 
R$^{2}$ & 0.557 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

@@

Our findings provide interesting insights into the effect that LSMPAs
can have on vessel behavior and the redistribution of fishing effort.
These collection of results shows that the implementation of PIPA caused
treated vessels to redeuce their fishing hours, and that this effect is
greater for purse seiners than longliners. Even though treated vessels
fish less, their relative allocation of fishing hours increased for all
other fishing grouds. This does not imply that there is more fishing
effort exherted by treated vessels, but rather that each region receives
a greater portion of the post-PIPA fishing effort of these same vessels,
which is lower than pre-PIPA levels. In this section we discuss the
implications of vessel-level reductions in fishing effort and the
increase in relative allocation of the remaining effort through space.
We also provide plausible explanations as to why purse seiners seem to
be more reactive to the spatial closure.

Previous studies on insular environments suggest that vessels move to
distant places, which might be translated as increased costs
\citep{stevenson_2013}. Nevertheless, they do not use counterfactuals
that could help account for system- or fleet-level changes that occur
through time. Others have used similar satellite-tracking systems to
show that fishing effort accumulates near the edges ospatial closures,
yielding greater catches \citep{murawski_2005}. Yet, these vessel tracks
do not cover the pre-reserve period, making it difficult identify the
contribution of spatial closures to the observed spatial distribution of
fishing vessels. Recent work by \citet{elahi_2018} identified that total
fishing effort in a focal region where a short-term MPA was implemented
showed little change, likely indicating that fishers redistributed
fishing effort to compensate for the reduction in available space. Our
data is assambled in a similar way, with fishing positions before and
after the implementation of PIPA and vessels grouped into treated and
control groups. Our BACI design, along with our
difference-in-differences analysis allows us to make causal inferences
about the effect that large scale marine protected areas have on fishing
effort.

A major shortcomming of our analyses is that we do not observe catches
or revenues, which ultimately are the factors that guide the decission
making process of profit-maximizing agents. \textbf{Expandir aqui}

The different responses observed between purse seiners and longliners
might have two possible explanations. It is likely that PIPA did not
contain habitat that longliners would consider optimal. Therefore, the
sporadic fishing events that occurred there are of little importance to
the fleet, and it is unlikely that the implementation of PIPA has an
effect on them. Alternatively, the differences may be due to the nature
of each fishing gear. Purse seiners are often constrained by seafloor
and termocline depth, and have a smaller spatial footpring
\citep{kroodsma_2018}. Tuna purse seiners are known to have greater
proportion of null sets (\emph{i.e.} where the purse seine is
effectively casted arround tuna, but no catch is obtained) during El
Niño years, where the termocline deepens in the Eastern Pacific
\citep{dreyfusleon_2015}. On the other hand, longliners may be more
flexible as to where they can deploy their longlines.
\citet{ortuocrespo_2018} evaluated the ecological niche of the pelagic
longline fleet, and suggest that the fleet may be underutilizing the
ocean, meaning that they can easily redistribute elsewhere.
\textbf{Further research shoudl focus on identifying the implications.
So what? What happens?}

Que mas dice Elahi o Wizaka (fishing the line) en su discusion? Que
aportes tiene este trabajo????
